---
title: "librarytoC"
author: "Bernd Gruber"
date: "3 August 2017"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## How to change the R library folder at startup

Info: R uses the path that is provided by the ```.libPaths()``` function. You can check you current folder via:

```{r, eval=FALSE}
.libPaths()
```



This documents describes a simple way to change the directory folder at startup in R:

1.	Go to your R etc folder on C: (should be something like c:/Program Files/R/R-3.3.2/etc/
2.	Make sure there is not already a file called “Renviron.site”
3.	Copy the [**Renviron.site**](https://github.com/green-striped-gecko/rblog) file to that folder: c:/Program Files/R/R-3.3.2/etc/
4.	If you have already a file called Renviron.site (this is a text file open it with wordpad, notepad whatever text editor and simply add the single line that is in the file, namely: 

R_LIBS='C:/PROGRAM FILES/R/library'


5.  Create an empty folder called library at the location specified in the file (e.g. C:/PROGRAM FILES/R/). Note you may need to change the write access of the library folder (so R is allowed to write to that folder) using the normal Windows method (or whatever system you are working with). For Windows: Right click on the folder in the Explorer, select the Security tab and change the permissons for that folder to be writable for the intended user.

6.	Restart R studio and now your path to the library is c:/program files/R/library 
7.	You can check that via typing

```{r}
.libPaths()[1]
```



